Real-space computation of $E$/$B$-mode maps I: Formalism, Compact Kernels, and Polarized Filaments

### 2018-07-30 articles/formalism/sections/generalizedeb.tex
removed text change highlights and added acknowledgements

%--------------------------------------------------------
\paragraph{Relation to the spin raising $\eth^2$ and lowering $\bar{\eth}^2$ operators.}
Recall that on operating twice with the spin lowering operator on the Stokes charge ${}_{+2}X$ results in filtered version of $E/B$ maps as in \eq{eq:ebdef}. Now note that it is possible to construct a modified real space operator by choosing the harmonic space function to be $g_{\ell} = ({(\ell+2)!/(\ell-2)!})^{1/2}$, resulting in similarly filtered $E/B$ maps as follows:
%
\beq 
[\mathcal{E} + i \mathcal{B}](\hat{n}_e)=- \Delta \Omega\sum_{q=1}^{N_{\rm pix}} \Bigg\lbrace  \left[  \sum_{\ell=\ell_{\rm min}}^{\ell_{\rm max}} \frac{2 \ell+1}{4 \pi} P_{\ell}^2(\beta_{qe}) \right] e^{-i2\alpha_{eq}} {}_{+2}X(\hat{n}_{q}) \Bigg\rbrace \,. \label{eq:bl_ebdef_lower} 
\eeq
%
Comparing to \eq{eq:ebdef_lower} makes apparent the following mapping:
%
\beq
\bar{\eth}^2_{\textrm BL} \equiv \Delta \Omega \sum_{q=1}^{N_{\rm pix}} \left[ \sum_{\ell=\ell_{\rm min}}^{\ell_{\rm max}} \frac{2 \ell+1}{4 \pi} P_{\ell}^2(\beta_{qe}) \right] e^{-i2\alpha_{eq}}\,,
\eeq
%
\revisit{where $\bar{\eth}^2_{\textrm BL}$ denotes the band limited spin lowering operator, thats relevant in the case of a discretely sampled spin-2 field on the sphere. In the limit of $\ell_{\rm max} \rightarrow \infty$, the $\bar{\eth}^2_{\textrm BL} \rightarrow \bar{\eth}^2$.}
%The operator $\bar{\eth}^2_{\textrm BL}$ is composed of derivative operations and hence has an implicit positional dependence for all numerical purposes which is made explicit in the band limited version of the operator.  
The band limited version of the spin raising operator $\eth^2$ is derived by simply taking the conjugate of the above equation.
%--------------------------------------------------------

>>>>

%--------------------------------------------------------
\paragraph{Relation to the spin raising $\eth^2$ and lowering $\bar{\eth}^2$ operators.}
Recall that on operating twice with the spin lowering operator on the Stokes charge ${}_{+2}X$ results in filtered version of $E/B$ maps as in \eq{eq:ebdef}. Now note that it is possible to construct a modified real space operator by choosing the harmonic space function to be $g_{\ell} = ({(\ell+2)!/(\ell-2)!})^{1/2}$, resulting in similarly filtered $E/B$ maps as follows:
%
\beq 
[\mathcal{E} + i \mathcal{B}](\hat{n}_e)=- \Delta \Omega\sum_{q=1}^{N_{\rm pix}} \Bigg\lbrace  \left[  \sum_{\ell=\ell_{\rm min}}^{\ell_{\rm max}} \frac{2 \ell+1}{4 \pi} P_{\ell}^2(\beta_{qe}) \right] e^{-i2\alpha_{eq}} {}_{+2}X(\hat{n}_{q}) \Bigg\rbrace \,. \label{eq:bl_ebdef_lower} 
\eeq
%
Comparing to \eq{eq:ebdef_lower} makes apparent the following mapping:
%
\beq
\bar{\eth}^2_{\textrm BL} \equiv \Delta \Omega \sum_{q=1}^{N_{\rm pix}} \left[ \sum_{\ell=\ell_{\rm min}}^{\ell_{\rm max}} \frac{2 \ell+1}{4 \pi} P_{\ell}^2(\beta_{qe}) \right] e^{-i2\alpha_{eq}}\,,
\eeq
%
where we use the notation $\bar{\eth}^2_{\textrm BL}$ to represent the band limited version of the spin lowering operator, thats relevant in the case of a discretely sampled spin-2 field on the sphere. In the limit of $\ell_{\rm max} \rightarrow \infty$, the $\bar{\eth}^2_{\textrm BL} \rightarrow \bar{\eth}^2$.
The band limited version of the spin raising operator $\eth^2$ is derived by simply taking the conjugate of the above equation.
%--------------------------------------------------------
